### 2016-12-29 paper/paper.tex
abstract tweak

\paragraph{Abstract:}
% Context
Stellar photospheres, to first order, have their spectral properties
set by the local quantities (spectroscopic parameters) effective
temperature, surface gravity, and metallicity (chemical composition);
As their name suggests, spectroscopic parameters can be determined
with stellar spectra and photosphere models.
Global stellar structure, including radii, masses, and bolometric
luminosities cannot be predicted theoretically without a physical
model of stellar structure or stellar evolution.
The \Gaia\ Mission has already delivered parallaxes---and therefore
luminosity information---for millions of stars; \GALEX\ and
\APASS\ deliver multi-band photometry; for a subset, \RAVEon\ delivers
spectroscopic parameters.
% Aims
In this project, we infer spectroscopic parameters for stars for which
only photometry and astrometry is available.
We make no use of stellar structure or evolution models.
% Methods
After showing empirically that stars with similar luminosities and
colors have similar spectroscopic parameters, we train a very flexible
regression model of the relationship between luminosity, color, and
the spectroscopic parameters.
The model is a modification of a k-nearest-neighbors method.
We use this model to paint spectroscopic parameters onto stars that have
not been observed spectroscopically.
% Results
We find XXX and YYY. Things degrade in ZZZ way when WWW.

>>>>

\paragraph{Abstract:}
% Context
Stellar photospheres, to first order, have their spectral properties
set by the local quantities (spectroscopic parameters) effective
temperature, surface gravity, and metallicity (chemical composition);
As their name suggests, spectroscopic parameters can be determined
with (medium to high resolution) spectral data and photosphere models.
Global stellar structure, including radii, masses, and bolometric
luminosities cannot be predicted theoretically without a physical
model of stellar structure or stellar evolution.
The \Gaia\ Mission has already delivered parallaxes---and therefore
luminosity information---for millions of stars; \GALEX\ and
\APASS\ deliver multi-band photometry; for a subset, \RAVEon\ delivers
spectroscopic parameters.
% Aims
In this project, we infer spectroscopic parameters for stars for which
only photometry and astrometry is available.
We make no use of stellar structure or evolution models.
% Methods
After showing empirically that stars with similar luminosities and
colors have similar spectroscopic parameters, we train a very flexible
regression model of the relationship between luminosity, color, and
the spectroscopic parameters.
The model is a modification of a k-nearest-neighbors method.
We use this model to paint spectroscopic parameters onto stars that have
not been observed spectroscopically.
% Results
We find XXX and YYY. Things degrade in ZZZ way when WWW.
